---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rmdpartials
[![Travis-CI Build Status](https://travis-ci.org/rubenarslan/rmdpartials.svg?branch=master)](https://travis-ci.org/rubenarslan/rmdpartials) 
[![codecov](https://codecov.io/gh/rubenarslan/rmdpartials/branch/master/graph/badge.svg)](https://codecov.io/gh/rubenarslan/rmdpartials)

_Simplify using rmarkdown partials to document objects in R_

## Description

Ever want to make a standardized way to report a summary of something like a regression, but did not want to limit yourself to one unformatted block of text, one table, or one figure?

Rmarkdown partials allow you to define standardised knitr code chunks that become part of your rmarkdown report. They can then be turned into HTML,
PDFs, or Word files. You could, for example, create an rmarkdown partial to summarise regression models in a flexible way.

You can also define your partials as methods of `knit_print`, so that a rich rmarkdown partial is made by default.

## Documentation
Confer the help or: https://rubenarslan.github.io/rmdpartials.
See the [vignette](https://rubenarslan.github.io/rmdpartials/articles/rmdpartials.html) for a quick example of an HTML document generated with `rmdpartials`.

## Install

To get the latest development version:

```r
install.packages("remotes")
remotes::install_github("rubenarslan/rmdpartials")
```

## Define a partial
Define a function like this:

```r
my_summary <- function(object) {
  rmdpartials::partial("_my_summary.Rmd")
}
```

And create a file called `_my_summary.Rmd` with contents like this:

````
## My special summary

```{r}`r ''`
summary(object)
```

## My special plot
```{r}`r ''`
plot(object)
```
````

## Usage

To use the partial in an rmarkdown report

````
```{r}`r ''`
m1 <- lm(y ~ x, data = data)
my_summary(m1)
```
````

### Usage as a knit_print method
To make your partial the default printing option for objects of a certain class
when they are echoed in a knitr document, give it the name of a knit_print method.

```r
knit_print.lm <- function(object) {
  rmdpartials::partial("_my_summary.Rmd")
}
```

Now, all you need to is let the lm object be echoed.

````
```{r}`r ''`
m1 <- lm(y ~ x, data = data)
m1
```
````

You can also preview what the result from the partial would look like
by calling it in an interactive session.

## [Code of conduct for contributing](https://rubenarslan.github.io/rmdpartials/CONDUCT.html)
