```{r rmdpartialsetup,eval=TRUE,echo=FALSE}
if (exists("testing")) {
  data("ChickWeight")
  regression <- lm(weight ~ Time, data = ChickWeight)
}
```

# Merge info

There are <big>`r x_duplicates`</big> duplicated rows in `r x_name` out of `r x_rows` total rows.

There are <big>`r y_duplicates`</big> duplicated rows in `r y_name` out of `r y_rows` total rows.

<details>
<summary>`r nrow(in_x_and_y)` rows overlap between `r x_name` and `r y_name`</summary>


```{r}
if (nrow(in_x_and_y) > 200) {
  in_x_and_y <- head(in_x_not_y, 200)
  message("Only first 200 rows shown")
}
DT::datatable(in_x_and_y, filter = "top",
              rownames = FALSE)
```


</details>

<details>
<summary>`r nrow(in_x_not_y)` rows are in `r x_name` but have no corresponding rows in `r y_name`</summary>

```{r}
if (nrow(in_x_not_y) > 200) {
  in_x_not_y <- head(in_x_not_y, 200)
  message("Only first 200 rows shown")
}
DT::datatable(in_x_not_y, filter = "top",
              rownames = FALSE)
```

</details>

<details>
<summary>`r nrow(in_y_not_x)` rows are in `r y_name` but have no corresponding rows in `r x_name`</summary>

```{r}
if (nrow(in_y_not_x) > 200) {
  in_y_not_x <- head(in_y_not_x, 200)
  message("Only first 200 rows shown")
}
DT::datatable(in_y_not_x, filter = "top",
              rownames = FALSE)
```

</details>

<script>
  $(function() {
    $('details').on('toggle', function() {
      if(this.open) {
        // jquery $('window').resize or $('window').trigger('resize') do not work
        window.dispatchEvent(new Event('resize'));
      }
    })
  })
</script>
