---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rmdpartials
[![Travis-CI Build Status](https://travis-ci.org/rubenarslan/rmdpartials.svg?branch=master)](https://travis-ci.org/rubenarslan/rmdpartials) 
[![codecov](https://codecov.io/gh/rubenarslan/rmdpartials/branch/master/graph/badge.svg)](https://codecov.io/gh/rubenarslan/rmdpartials)

[![CRAN status](http://www.r-pkg.org/badges/version-ago/rmdpartials)](https://cran.r-project.org/package=rmdpartials)
![Downloads](https://cranlogs.r-pkg.org/badges/grand-total/rmdpartials)
[![DOI](https://zenodo.org/badge/109252375.svg)](https://zenodo.org/badge/latestdoi/109252375)

_Simplify using rmarkdown partials to document objects in R_

## Description

Ever want to make a standardized way to report a summary of something like a regression, but did not want to limit yourself to one unformatted block of text, one table, or one figure?

Rmarkdown partials allow you to define standardised knitr code chunks that become part of your rmarkdown report. They can then be turned into HTML,
PDFs, or Word files. You could, for example, create an rmarkdown partial to summarise regression models in a flexible way.

You can also define your partials as methods of `knit_print`, so that a rich rmarkdown partial is made by default.

## Documentation
Confer the help or: https://rubenarslan.github.io/rmdpartials.
See the [vignette](https://rubenarslan.github.io/rmdpartials/articles/rmdpartials.html) for a quick example of an HTML document generated with `rmdpartials`.

## Use locally
### Install

Run the following in R.
```r
install.packages("rmdpartials")
```

To get the latest development version:

```r
install.packages("remotes")
remotes::install_github("rubenarslan/rmdpartials")
```


```{r}`r ''`
m1 <- lm(y ~ x, data = data)
your_partial(m1)
```
````

## [Code of conduct for contributing](CONDUCT.md)
